ESBMC-GPU \\ A Context-Bounded Model Checking Tool \\ to Verify CUDA Programs

### 2017-05-11 Publications/Original Software Publications/Science of Computer Programming/source/manuscript.tex
fixing typos on page 6
Signed-off-by: Felipe R. Monteiro <rms.felipe@gmail.com>

{\bf Performance.} MPOR resulted in a performance improvement of approximately $80\%$, by decreasing the verification time from $16$ to $3$ hours, while the two-threads analysis further reduced that to $789.6$ sec. Although such techniques have considerably improved the ESBMC-GPU's performance, it still takes longer than the other evaluated tools: GPUVerify ($98.36$ sec), GKLEE ($108.32$ sec), and CIVL ($708.52$ sec). This is due to thread interleavings, which combine symbolic model checking with explicit state-space exploration~\cite{pereira:2016}. %In addition, even though ESBMC-GPU reports the highest verification time, it still presents the highest accuracy, with less than $6$ seconds per benchmark.%, which shows that it is a feasible tool regarding the verification of CUDA-based applications. 
In addition, ESBMC-GPU still presents the highest accuracy, with less than $6$ seconds per benchmark.

@@

ESBMC-GPU marks the first application of an SMT-based context-BMC tool that recognizes CUDA directives~\cite{pereira:2016}. Besides, it further simplifies verification models and provides fewer incorrect results, if compared with GKLEE, GPUVerify, and CIVL. Finally, it presents improved ability to detect array out-of-bounds and data race violations. Future work aims to support stream interleaving and implement further techniques to reduce the number of thread interleavings, by taking into account GPU symmetry.

>>>>

{\bf Performance.} MPOR resulted in a performance improvement of approximately $80\%$, by decreasing the verification time from $16$ to $3$ hours, while the two-threads analysis further reduced that to $789.6$ sec. Although such techniques have considerably improved the ESBMC-GPU's performance, it still takes longer than the other evaluated tools: GPUVerify ($98.36$ sec), GKLEE ($108.32$ sec), and CIVL ($708.52$ sec). This is due to thread interleavings, which combine symbolic model checking with explicit state-space exploration~\cite{pereira:2016}. %In addition, even though ESBMC-GPU reports the highest verification time, it still presents the highest accuracy, with less than $6$ seconds per benchmark.%, which shows that it is a feasible tool regarding the verification of CUDA-based applications. 
On the other hand, ESBMC-GPU still presents the highest accuracy, with less than $6$ seconds per benchmark.

@@

ESBMC-GPU marks the first application of an SMT-based context-BMC tool that recognizes CUDA directives~\cite{pereira:2016}. Besides, it further simplifies verification models and provides fewer incorrect results, compared with GKLEE, GPUVerify, and CIVL. Finally, it presents improved ability to detect array out-of-bounds and data race violations. Future work aims to support stream interleaving and implement further techniques to reduce the number of thread interleavings, by taking into account GPU symmetry.
